The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-07-01 manuscript/manuscript0627.tex
Edit before back to China.

To avoid any systematic bias between samples in the literature, we compare the recipes implemented in \citet{Schulze2018} and \citet{Ding2017b}. We find that the \hbeta\ estimator is very consistent (\mbh\ r.m.s. $<0.03$~dex) between the two reference samples. We also find that the cross-calibration between the \halpha\ and \hbeta\ has better agreement in \citet{Schulze2018}. Thus, we adopt the scheme given in \citet{Schulze2018} that is based on the recalibration of these relations using luminous quasars out to high redshift \citep{Jun2015} :

@@

We include in our analysis published samples at intermediate redshifts to understand the evolution of these correlations. We select samples that were analyzed by members of our team, in order to ensure uniform measurements. The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$. In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample. Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh}. For \mbh\ estimated from \Mgii\, we adopt the recipe by \citet{Ding2017b}.

>>>>

{\color{red} To avoid any systematic bias between samples in the literature, we aim to adopt a class of self-consistent estimators for our sample. We first compare the estimators implemented in \citet{Schulze2018} to the self-consistent ones in \citet{Ding2017b}, and find that their \hbeta(FWHM(5100)) estimators are very consistent (\mbh\ r.m.s. $<0.03$~dex). However, there is a $\sim~0.2$ dex inconsistency in their \halpha\ estimators. Thus, we adopt all the AGNs in \citet{Schulze2018} which have both \halpha\ and \hbeta\ lines (35 AGNs in total) and carry out a cross-calibration to select the \halpha\ estimator which has better consistency. The result show that the \halpha\ estimators in \citet{Schulze2018} demonstrate the better agreement, which are adopted by this work:
%Thus, we adopt the scheme given in \citet{Schulze2018} that is based on the recalibration of these relations using luminous quasars out to high redshift \citep{Jun2015} :

\begin{figure}
\centering
{
\includegraphics[height=0.55\textwidth]{fig/cross-calibrate.pdf}
}
\caption{\label{fig:cross-calibrate} 
Cross-calibration using the AGNs in \citet{Schulze2018} for \halpha\ and \hbeta\ estimators. The \citet{Schulze2018} demonstrate better agreement (\mbh\ mean offset $\sim~0.09$~dex) than \citet{Ding2017b} (\mbh\ mean offset $\sim~0.27$~dex). {\bf Xuheng: The Jun+2015's recipe has a 0.4 dex mismatch in this comparison.}}
\end{figure} 
}

@@

We include in our analysis published samples at intermediate redshifts to understand the evolution of these correlations. We select samples that were analyzed by members of our team, in order to ensure uniform measurements. The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$. In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample.

{\color{red} For all the comparison AGN samples, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh}. For \mbh\ estimated using \Mgii\ and  \hbeta$(\sigma_{\rm H\beta})$ lines, we adopt the recipes by \citet{Ding2017b}. }
